Template for preparing your Brief Report submission to PNAS using Overleaf

### 2023-11-22 PNAS/index.Rnw

As we develop objective algorithms and standardize laboratory procedures in forensic pattern evidence, we must remain cognizant that we often are conducting many comparisons, either implicitly or explicitly. Algorithms in pattern evidence often utilize cross-correlation \citep{vorburgerApplicationsCrosscorrelationFunctions2011} to align different data sources, implicitly making comparisons along the entire length or surface of the data. Similarly, forensic examiners visually rotate or align two pieces of evidence under comparison microscopes. Similarly, when we conduct database searches, these searches often return the $N$ best matches from the database, but this requires making comparisons to all of the database entries which meet the search criteria.

>>>>

As we develop objective algorithms and standardize laboratory procedures in forensic pattern evidence, we must remain cognizant that a single conclusion is often based on  many comparisons, either implicitly or explicitly. \hh{Algorithms, in particular, make a large number of comparisons out of a user's sight. The cross-correlation function, for example, has been suggested \citep{vorburgerApplicationsCrosscorrelationFunctions2011} as one of the first quantitative measures in response to the NAS report (cite!!!), and is used in most pattern searching algorithms to 'find the best' alignment between two sources and also evaluate the overall similarity. }  %Algorithms in pattern evidence often utilize cross-correlation \citep{vorburgerApplicationsCrosscorrelationFunctions2011} to align different data sources, implicitly making comparisons along the entire length or surface of the data.
\hh{'Finding the best' requires implicitly to slide one source across the whole length (for one-dimensional sources, such as striations) or area (for two dimensional sources, such as impression marks) of the other source and keep track of the similarity measure. }

Similarly, forensic examiners visually rotate or align two pieces of evidence under comparison microscopes. When we conduct database searches, these searches often return the $N$ best matches from the database, but this requires making comparisons to all of the database entries which meet the search criteria.
